cumentclass[11pt,a4paper]{moderncv}

\moderncvtheme[black]{classic}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}

\firstname{Jonathan}
\familyname{\mbox{Almeida}}
\title{\small Android $\star$ Python $\star$ Git $\star$ C/C++}

\email{me@jonalmeida.com}
\homepage{keybase.io/jonalmeida}
\social[linkedin]{jonalmeida}
\social[github]{jonalmeida}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}

% command and color used in this document, independently from moderncv
\definecolor{see}{rgb}{0.5,0.5,0.5}% for web links
\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}% for text subscripts
\renewcommand{\labelitemi}{$\circ$}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace*{-1cm}


\section{\textsc{Technical Skills}}
        \cvitem{\textbullet}{\textbf{Programming Languages}: Python, Java, C++, Javascript, Rust, Bash, Qt/QML}
        \cvitem{\textbullet}{\textbf{Frameworks \& Other}: Firebase, Parse, NodeJS, MySQL/SQLite}

\section{\textsc{GitHub Projects}}
        \cvitem{\textbullet}{\textbf{\href{http://github.com/jonalmeida/ws-p2p}{jonalmeida/ws-p2p}}}
        \vspace*{-0.15cm}
        \cvitem{}{
            {\footnotesize
                \begin{itemize}
                \item Peer-to-peer network with causally ordered messages using WebSockets with Rust.
                \end{itemize}
            }
        }
        \vspace*{-0.5cm}
        \cvitem{\textbullet}{\textbf{\href{http://github.com/vicinium/vicinium-android}{vicinium/vicinium-android}}}
        \vspace*{-0.15cm}
        \cvitem{}{
            {\footnotesize
                \begin{itemize}
                \item A micro location-based chat application for Android; like IRC, but location-based.
                \end{itemize}
            }
        }
        \vspace*{-0.5cm}
        \cvitem{\textbullet}{\textbf{\href{http://github.com/jonalmeida/hack-the-north-crazyflie}{jonalmeida/hack-the-north-crazyflie}}}
        \vspace*{-0.15cm}
        \cvitem{}{
            {\footnotesize
                \begin{itemize}
                \item Micro-quadcopter controlled with a Leap Motion controller.
                \end{itemize}
            }
        }
        \vspace*{-0.5cm}

\section{\textsc{Professional Experience}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
        \cventry{May. 2016 - Aug. 2016}{Firefox Mobile Intern}{Mozilla}{San Francisco}{}{
            {\footnotesize
                \begin{itemize}
                \item Designed and created a tab grouping app {\color{see}\href{https://air.mozilla.org/life-is-still-hard/}{(demo)}} for prototyping using machine learning.
                \item Developed custom layouts for the homescreen in Firefox for Android to show user activity {\color{see}\href{http://jonalmeida.com/resume/as\_panel.png}{(image)}}.
                \item Helped organize and attended a Design Sprint for location-based prototyping.
                \item Technologies got to work on:
                Android, Python
                \end{itemize}
            }
        }
        \cventry{June. 2015 - Sept. 2015}{Firefox Mobile Intern}{Mozilla}{San Francisco}{}{
            {\footnotesize
                \begin{itemize}
                \item "{\color{see} \href{http://www.ghacks.net/2015/09/30/firefox-for-android-gets-click-to-play-for-pictures/}{Click-to-view images}}" in Firefox for Android to reduce bandwidth usages.
                \item Setup a remote device farm for accessing un-used devices for a team spread across multiple offices.
                \item Converting {\color{see} \href{https://medium.com/@antlam/quick-search-bdd374257e75}{Quick Search}} ListView for more performant RecyclerView.
                \item Technologies got to work on:
                Android, Javascript
                \end{itemize}
            }
        }
        \cventry{May. 2014 - Aug. 2014}{Software Developer Intern}{Snowplow Analytics Ltd.}{}{}{
            {\footnotesize
                \begin{itemize}
                \item Created and modularized the Java event tracker; released {\color{see} \href{http://snowplowanalytics.com/tags.html\#java}{multiple version updates.}}
                \item Released the {\color{see} \href{http://snowplowanalytics.com/tags.html\#ios}{iOS}} and {\color{see} \href{http://snowplowanalytics.com/tags.html\#android}{Android}} trackers, inheriting from the Java core library.
                \item Managed and prioritized feature release schedules on GitHub; CI integration, etc.
                \end{itemize}
            }
        }
        \cventry{May. 2013 - Dec. 2013}{Software Developer Intern}{BlackBerry Ltd.}{}{}{
            {\footnotesize
                \begin{itemize}
                \item Single-handedly developed the {\color{see} \href{http://jonalmeida.com/resume/notification\_screenshots}{Notification Settings in Qt}} (not usually reserved for internship developers).
                \item Worked with QA and product teams to re-architecture to the new Settings UI requirements.
                \item Implemented deep linking for third-party applications to link to their Settings UI.
                \item Created a Jenkins automation build machine to run with Google Test test cases for it.
                \item Technologies got to work on:
                Qt/QML, C++, Jenkins, Bash
                \end{itemize}
            }
        }
        \cventry{May. 2012 - Dec. 2012}{Software Test Developer Intern}{BlackBerry Ltd.}{}{}{
            {\footnotesize
                \begin{itemize}
                \item Primary support for remote QA team with issues they would encounter during their testing.
                \item Investigation and verification into issues seen on an infrastructure level of development.
                \item Mentored junior co-ops on a daily basis with all the above mentioned tasks.
                \item Received an employee recognition award for working in multiple war rooms with other teams.
                \end{itemize}
            }
        }
        \cventry{Aug. 2011 - Apr. 2012}{I.T. Services Help Desk}{University of Windsor}{}{}{
            {\footnotesize
                \begin{itemize}
                \item Provided support for installation as well as solving technical issues over the phone or remotely.
                \item Technologies got to work on:
                Lotus Notes, Novell NetWare, Trend Micro
                \end{itemize}
            }
        }

\section{\textsc{Other Personal Projects}}
        \cvitem{\textbullet}{Held workshops for introductions to Git/version control.}
        \cvitem{\textbullet}{Technical Reviewer for Global Hackathon Seoul (reviewed 1000+ global applicants).}
        \cvitem{\textbullet}{Mentored at various hackathons: McHacks, WearHacks, UofTHacks, HackWesterm, etc.}

\section{\textsc{Education}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
\cventry{2016}{Bachelors of Science, Computer Science}{University of Windsor}{}{}{}


\end{document}
%% end of file `page.tex'.
